### 2022-01-15 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b126c68309ef23dd542c6e4aab525cfb6b98b32a 🚀

Following the definition of Dunne (2006), a metaweb is the ecological
network analogue to the species pool; specifically, it inventories
\emph{potential} interactions between species for a spatially delimited
area (and so captures the \(\gamma\) diversity of interactions). The
metaweb is not a prediction of the network at a specific point within
the spatial area it covers: it will have a different structure, notably
by having a larger connectance (see \emph{e.g.} Wood et al., 2015) and
complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
local networks. These local networks (capturing the \(\alpha\) diversity
of interactions) are a subset of the metaweb's species and interactions,
and have been called ``metaweb realizations'' (Poisot et al., 2015).
Differences between local networks and their metawebs are due to chance,
species abundance and co-occurrence, local environmental conditions, and
local distribution of functional traits, among others.

@@

>>>>

Following the definition of Dunne (2006), a metaweb is the ecological
network analogue to the species pool; specifically, it inventories
\emph{potential} interactions between species for a spatially delimited
area (and so captures the \(\gamma\) diversity of interactions). The
metaweb is not a prediction of the network at a specific point within
the spatial area it covers: it will have a different structure, notably
by having a larger connectance (see \emph{e.g.} Wood et al., 2015) and
complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
local networks. These local networks (capturing the \(\alpha\) diversity
of interactions) are a subset of the metaweb's species and interactions,
and have been called ``metaweb realizations'' (Poisot et al., 2015).
Differences between local networks and their metawebs are due to chance,
species abundance and co-occurrence, local environmental conditions, and
local distribution of functional traits, among others. Yet, recent
results by Saravia et al. (2021) strongly suggest that the local
realizations only respond weakly to local conditions: instead, they
reflect constraints inherited by the structure of their metaweb. This
establishes the metaweb structure as the core goal of predictive network
ecology, as it is a required information to accurately produce
downscaled, local predictions.

@@

\leavevmode\hypertarget{ref-Saravia2021EcoNet}{}%
Saravia, L. A., Marina, T. I., Kristensen, N. P., De Troch, M., \& Momo,
F. R. (2021). Ecological network assembly: How the regional metaweb
influences local food webs. \emph{Journal of Animal Ecology},
\emph{n/a}(n/a). \url{https://doi.org/10.1111/1365-2656.13652}
